Presentation Title

### 2017-10-31 paper/s1-intro.tex
Address unfair facilitator election

\textbf{Related work.\quad}
Many approaches exist for improving the scalability of early blockchain systems.
Off-chain transactions make use of the fact that if nodes make frequent transactions,
then it is not necessary to store every transaction on the blockchain,
only the net settlement is needed.
The best examples are Lightning Network~\cite{lightningnetwork} and Duplex Micropayment Channels~\cite{decker2015fast}.
It promises significant scalability improvements, but complicates user experience and leads to centralisation.
Each node must deposit a suitable amount of Bitcoins into a multi-signature account.
A low deposit would not allow large transactions.
A high deposit locks the user from using much of her Bitcoins outside the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Moreover, creating channels with sufficient balance and also keeping it online to act as a router is expensive.
A casual user is not capable of such tasks, leading to centralisation.
% TODO other side-chain schemes? polkadot? perum? dfinity?

>>>>

\textbf{Related work.\quad}
Many approaches exist for improving the scalability of early blockchain systems.
Off-chain transactions make use of the fact that if nodes make frequent transactions,
then it is not necessary to store every transaction on the blockchain,
only the net settlement is needed.
The best examples are Lightning Network~\cite{lightningnetwork} and Duplex Micropayment Channels~\cite{decker2015fast}.
It promises significant scalability improvements, but complicates user experience and leads to centralisation.
That is, each node must deposit a suitable amount of Bitcoins into a multi-signature account.
A low deposit would not allow large transactions.
A high deposit locks the user from using much of their Bitcoins outside the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Moreover, creating channels with sufficient balance and also keeping it online to act as a router is expensive.
A casual user is not capable of such tasks, leading to centralisation.
% TODO other side-chain schemes? polkadot? perum? dfinity?

### 2017-10-31 paper/s2-problem.tex
Address unfair facilitator election

Note that the agreement property is similar, but a relaxed version of what is often seen in a Byzantine consensus problem.
Namely, the property only holds if honest nodes do not output \emph{unknown}.
For example, for a transaction, it is OK if two honest nodes output \emph{valid} and \emph{unknown}, but it is not OK to output \emph{valid} and \emph{invalid}.
Our problem does not have a termination property, also known as liveness.
Instead, nodes are incentivised to complete the protocol execution otherwise they risk economical loss;
we describe this phenomenon in~\Cref{sec:correctness-of-validity}.

The problem is purposefully made to be application neutral,
i.e. there are no constraints on the semantics of transactions.
This formulation is so that the protocol can act as a building block to many applications.
Due to this fact, we also do not consider global fork prevention or detection,
as some application may not need such strong guarantees such as the accounting of internet traffic in Tribler~\cite{pimotte, pouwelse2008tribler}.
On the other hand, we give two alternative constructions that do have fork detection in~\Cref{sec:fork}.
% TODO our transactions are rather different from a typical cryptocurrency transaction,
% should we still call it transactions or something else?

>>>>

Note that the agreement property is similar, but a relaxed version of what is often seen in a Byzantine consensus problem.
Namely, the property only holds if honest nodes do not output \emph{unknown}.
For example, for a transaction, it is fine if two honest nodes output \emph{valid} and \emph{unknown}, but it is not fine to output \emph{valid} and \emph{invalid}.
Our problem does not have a termination property.
Instead, nodes are incentivised to complete the protocol execution otherwise they risk economical loss;
we describe this phenomenon in~\Cref{sec:correctness-of-validity}.

The problem is purposefully made to be application neutral,
i.e. there are no constraints on the semantics of transactions.
This formulation is so that the protocol can act as a building block to many applications.
Due to this fact, we also do not consider global fork prevention or detection,
as some application may not need such strong guarantees such as the accounting of internet traffic in Tribler~\cite{pimotte, pouwelse2008tribler}.
On the other hand, we give two alternative constructions that do perform fork detection in~\Cref{sec:fork}.
% TODO our transactions are rather different from a typical cryptocurrency transaction,
% should we still call it transactions or something else?

### 2017-10-31 paper/s3-system.tex
Address unfair facilitator election

Early blockchain systems that use a global ledger are difficult to scale because every node must reach consensus on all the transactions that ever existed.
Instead, we introduce an alternative architecture where every node has their own genesis block and hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chains.
Transactions are stored in TX blocks, and every block only contains one transaction.
A transaction between two nodes should, therefore, result in two TX blocks on their respective hash chains.
We introduce a special block called checkpoint (CP) block,
which represents the state of a hash chain in the form of a hash pointer.
Then, a collection of CP blocks from all nodes would represent the state of the whole system.
A visualisation can be seen in~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the data structure used in \textsc{Checo}.
$t_{u, i}$ represents a TX block on $u$'s chain with a sequence number $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number $j$.
The blocks at the ends of the dotted lines are pairs of each other.
Blocks of sequence number 0 (e.g., $t_{c, 0}$) are genesis blocks.}
\label{fig:trustchain-good-cp}
\end{figure}

\textsc{Checo} consists of three protocols---consensus protocol, transaction protocol and validation protocol---all interacting with the distributed hash chain data structure described above.
The primary protocol is the consensus protocol,
which can be seen as a technique of running infinitely many times of an existing Byzantine consensus algorithm (in this work we use asynchronous common subset from HoneyBadgerBFT~\cite{miller2016honey}),
starting a new execution immediately after the previous one is completed.
Nodes create new CP blocks at the end of every execution.
This approach is necessary because blockchain systems always need to reach consensus on new values proposed by the nodes in the system,
or CP blocks in our case.

@@

For brevity, we left out issues such as selecting facilitators in a fair way and the exact validity condition.
The following sections give the formal description and will answer these issues.

@@

\begin{definition}
\textbf{Transaction block}

The TX block is a six-tuple, i.e
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message,
    which can be seen as an arbitrary string.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
% The fact that we have no constraint on the content of $m$ is in alignment with our problem description---application neutrality.

@@

\begin{definition}
\textbf{Checkpoint block and genesis block}

The CP block is a five-tuple, i.e. 
$$c_{u, i} = \langle \textsf{H}(b_{u, i-1}), seq_u, \textsf{H}(\C_r), r, sig_u \rangle,$$
where $\C_r$ is the consensus result (which we describe next in \Cref{sec:consensus-result}) in round $r$,
the other items are the same as the TX block definition.

@@

\begin{definition}
\label{sec:consensus-result}
\textbf{Consensus result}

Our consensus protocol runs in rounds,
where the first round is defined to be 1 and it is incremented after every execution of the consensus protocol.
The consensus result, output of the consensus protocol, is a tuple, i.e. 
$$\C_r = \langle r, C \rangle,$$
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

@@

\begin{definition}
\textbf{Enclosure and agreed enclosure}

If there exists a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$, where
\begin{itemize}
\item $c_{u, a}$ is the closest CP block to $t_{u, i}$ with a lower sequence number and
\item $c_{u, b}$ is the closest CP block to $t_{u, i}$ with a higher sequence number,
\end{itemize}
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Some TX blocks may not have any enclosure, then their enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

\begin{definition}
\textbf{Fragment and agreed fragment}

If the enclosure of some TX block $t_{u, i}$ is $\langle c_{u,a}, c_{u, b} \rangle$,
then its fragment $F_{u, i}$ is defined as $\{ b_{u, i} : a \le i \le b \}$.
Similarly, agreed fragment has the same definition as fragment but using agreed enclosure.
For convenience, the function $\textsf{agreed\_fragment}(t_{u, i})$ outputs the agreed fragment of $t_{u, i}$ if it exists, otherwise $\bot$.
\end{definition}

\subsection{Consensus Protocol}
Our scalable consensus protocol $\Pi_c$ uses an unmodified asynchronous common subset (ACS) algorithm as the key building block.
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
We formally define the desired properties below.
\begin{definition}
\label{def:consensus}
\textbf{\textsc{Checo} consensus protocol}

A \textsc{Checo} consensus protocol is correct if the following holds for every round $r$.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}, and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}

\subsubsection{Bootstrap Phase}
\label{sec:bootstrap}
To bootstrap, imagine that there is some bootstrap oracle that initiates the correct program on every node,
meaning that it satisfied the properties in \Cref{def:consensus}.
In practice, the bootstrap oracle is most likely the software developer that sets up the system and assigns the facilitators of round 1 in a fair way.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

@@

The core of the consensus phase is the ACS algorithm,
which is derived from HoneyBadgerBFT~\cite{miller2016honey}.
We do not use the full HoneyBadgerBFT due to the following.
First, the transactions in HoneyBadgerBFT are first queued in a buffer and the main consensus algorithm starts only when the buffer reaches an optimal size.
We do not have an infinite stream of CP blocks, thus buffering is unsuitable.
Second, HoneyBadgerBFT uses threshold encryption to hide the content of the transactions.
But we do not reach consensus on transactions, only CP blocks, so hiding CP blocks is meaningless for us.

@@

Upon receiving $\C_{r + 1}$ and at least $n - t$ valid signatures, $u$ performs two tasks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1})$ (\Cref{alg:new-cp}).
Second, it computes the new facilitators using $\textsf{get\_facilitator}(\C_{r + 1}, n)$ (\Cref{alg:facilitator}),
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the state at the beginning of the consensus phase,
so a new round can be started.

@@

The TX protocol $\Pi_t$, shown in \Cref{alg:tx-proto}, is run by all nodes.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$.
Then the initiator sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

A key feature of $\Pi_t$ is that it is non-blocking.
At no time in \Cref{alg:new-tx} or \Cref{alg:tx-proto} do we need to hold the chain state and wait for some message to be delivered before committing a new block to the chain.
This allows for a high level of concurrency where we can call $\textsf{new\_tx}(\cdot)$ and send \texttt{tx\_req} messages multiple times without waiting for the corresponding \texttt{tx\_resp} messages.

@@

\subsubsection{Validity Definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$,
the validity of the TX block $t_{u, i}$ with its corresponding fragment $F_{u, i}$ is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ (\Cref{alg:get-validity}).
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve because typically the caller is $u$,
so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

@@

\subsubsection{Validation Protocol}
Our validation protocol $\Pi_v$,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties are as follows.
\begin{definition}
\label{def:validation}
\textbf{\textsc{Checo} validation protocol}

A \textsc{Checo} validation protocol is correct if the following properties hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If any correct node decides on the validity of a transaction, except when it is \emph{unknown},
        then all other correct nodes are able to reach the same conclusion or decide \emph{unknown}.
    \item \emph{Validity}:
        The validation protocol outputs the correct result
        according to the validity definition above.
    % \item \emph{Unforgeability}:
    %     If some transaction is valid, it cannot be forged into an invalid transaction.
    %     If some transaction is invalid, it cannot be forged into a valid transaction.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as valid (invalid) eventually.
\end{enumerate}
\end{definition}

@@

>>>>

Early blockchain systems that use a global ledger are difficult to scale because every node must reach consensus on all the transactions that ever existed.
Instead, we introduce an alternative architecture where every node has their own genesis block and hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chains.
Transactions are stored in TX blocks, and every block only contains one transaction.
A transaction between two nodes should, therefore, result in two TX blocks on their respective hash chains.
We introduce a special block called checkpoint (CP) block,
which represents the state of a hash chain in the form of a hash pointer.
Then, a collection of CP blocks from all nodes would represent the state of the whole system.
A visualisation can be seen in~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the data structure used in \textsc{Checo}.
$t_{u, i}$ represents a TX block on $u$'s chain with a sequence number $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number $j$.
The blocks at the ends of the dotted lines are pairs of each other.
Blocks of sequence number 0 (e.g., $c_{c, 0}$) are genesis blocks.}
\label{fig:trustchain-good-cp}
\end{figure}

\textsc{Checo} consists of three protocols---consensus protocol, transaction protocol and validation protocol---all interacting with the distributed hash chain data structure described above.
The primary protocol is the consensus protocol,
which can be seen as a technique of running infinitely many times of an existing Byzantine consensus algorithm (in this work we use the asynchronous common subset protocol described in HoneyBadgerBFT~\cite{miller2016honey}),
starting a new execution immediately after the previous one is completed.
Nodes create new CP blocks at the end of every execution.
This approach is necessary because blockchain systems always need to reach consensus on new values proposed by the nodes in the system,
or CP blocks in our case.

@@

The following sections give the formal description.

@@

\begin{definition}[Transaction block]
The TX block is a six-tuple, i.e
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message,
    which can be seen as an arbitrary string.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
% The fact that we have no constraint on the content of $m$ is in alignment with our problem description---application neutrality.

@@

\begin{definition}[Checkpoint block and genesis block]
The CP block is a five-tuple, i.e. 
$$c_{u, i} = \langle \textsf{H}(b_{u, i-1}), seq_u, \textsf{H}(\C_r), r, sig_u \rangle,$$
where $\C_r$ is the consensus result (which we describe next in \Cref{sec:consensus-result}) in round $r$,
the other items are the same as the TX block definition.

@@

\begin{definition}[Consensus result]
\label{sec:consensus-result}
Our consensus protocol runs in rounds,
where the first round is defined to be 1 and it is incremented after every execution of the consensus protocol.
The consensus result, output of the consensus protocol, is a tuple, i.e. 
$$\C_r = \langle r, C \rangle,$$
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

@@

\begin{definition}[Enclosure and agreed enclosure]
If there exists a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$, where
\begin{itemize}
\item $c_{u, a}$ is the closest CP block to $t_{u, i}$ with a lower sequence number and
\item $c_{u, b}$ is the closest CP block to $t_{u, i}$ with a higher sequence number,
\end{itemize}
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Some TX blocks may not have any enclosure, then their enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

\begin{definition}[Fragment and agreed fragment]
If the enclosure of some TX block $t_{u, i}$ is $\langle c_{u,a}, c_{u, b} \rangle$,
then its fragment $F_{u, i}$ is defined as $\{ b_{u, i} : a \le i \le b \}$.
Similarly, agreed fragment has the same definition as fragment but using agreed enclosure.
For convenience, the function $\textsf{agreed\_fragment}(t_{u, i})$ outputs the agreed fragment of $t_{u, i}$ if it exists, otherwise $\bot$.
\end{definition}

\subsection{Consensus Protocol}
Our scalable consensus protocol $\Pi_c$ uses an asynchronous common subset (ACS) protocol as the key building block.
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
We formally define the desired properties below.
\begin{definition}[\textsc{Checo} consensus protocol]\label{def:consensus}
A \textsc{Checo} consensus protocol is correct if the following holds for every round $r$.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}, and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}

\subsubsection{Bootstrap Phase}
\label{sec:bootstrap}
To bootstrap, imagine that there is some bootstrap oracle that initiates the correct program on every node,
meaning that it satisfied the properties in \Cref{def:consensus}.
In practice, the bootstrap oracle is most likely the software developer that sets up the system and assigns the facilitators of round 1.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

@@

The core of the consensus phase is the ACS algorithm,
which is derived from HoneyBadgerBFT~\cite{miller2016honey}.
We do not use the full HoneyBadgerBFT due to the following.
First, the transactions in HoneyBadgerBFT are first queued in a buffer and the main consensus algorithm starts only when the buffer reaches an optimal size.
We do not have an infinite stream of CP blocks, thus buffering is unsuitable.
Second, HoneyBadgerBFT uses threshold encryption to hide the content of the transactions.
But we do not reach consensus on transactions, only CP blocks;
the content of the CP blocks are not sensitive so there is no need to hide it.

@@

Upon receiving $\C_{r + 1}$ and at least $n - t$ valid signatures, $u$ performs two tasks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1})$, described in \Cref{alg:new-cp}.
Second, it computes the new facilitators using $\textsf{get\_facilitator}(\C_{r + 1}, n)$, described in \Cref{alg:facilitator},
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the state at the beginning of the consensus phase,
so a new round can be started.

@@

The TX protocol $\Pi_t$, shown in \Cref{alg:tx-proto}, is run by all nodes.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$, described in \Cref{alg:new-tx}, with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$.
Then the initiator sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

A key feature of $\Pi_t$ is that it is non-blocking.
At no time in \Cref{alg:new-tx} or \Cref{alg:tx-proto} do we need to hold the chain state and wait for some message to be delivered before committing a new block to the chain.
This allows for a high level of concurrency where we can call many $\textsf{new\_tx}(\cdot)$ and send multiple \texttt{tx\_req} messages simultaneously without waiting for the corresponding \texttt{tx\_resp} messages.

@@

\subsubsection{Validity Definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$,
the validity of the TX block $t_{u, i}$ with its corresponding fragment $F_{u, i}$ is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ in \Cref{alg:get-validity}.
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve because typically the caller is $u$,
so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

@@

\subsubsection{Validation Protocol}
Our validation protocol $\Pi_v$,
shown in~\Cref{alg:vd-proto},
is designed to classify transactions according to the aforementioned validity definition.
If $u$ wishes to validate some TX with ID $txid$ and counterparty $v$, it sends $\langle \texttt{vd\_req}, txid \rangle$ to $v$.
The desired properties are as follows.
\begin{definition}[\textsc{Checo} validation protocol]\label{def:validation}
A \textsc{Checo} validation protocol is correct if the following properties hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If any correct node decides on the validity of a transaction, except when it is \emph{unknown},
        then all other correct nodes are able to reach the same conclusion or decide \emph{unknown}.
    \item \emph{Validity}:
        The validation protocol outputs the correct result
        according to the validity definition above.
    % \item \emph{Unforgeability}:
    %     If some transaction is valid, it cannot be forged into an invalid transaction.
    %     If some transaction is invalid, it cannot be forged into a valid transaction.
    \item \emph{Liveness}:
        Any valid (invalid) transaction is marked as valid (invalid) eventually.
\end{enumerate}
\end{definition}

@@

\subsection{Fair Facilitator Election}
Our consensus protocol does not guarantee fair facilitator election when dedicated attackers are present.
If a malicious facilitator is elected, it can delay, eavesdrop and collect all CP block messages before sending its own.
Effectively, it can predict the consensus result before the facilitators start the consensus protocol, and generate a CP block such that the malicious node has an unfair advantage of being elected as a facilitator in the next round.

To address the issue above,
the facilitators run an extra protocol after the consensus protocol to produce some unbiased randomness.
Concretely, they invoke RandHound~\cite{syta2017scalable} and then propagated the randomness and the signatures in the same way as the consensus result.
Upon receiving the randomness,
every node uses it in the hash function of \Cref{alg:facilitator} (i.e. $\textsf{H}(\text{randomness} || \C_r || pk \text{ of } x)$) to compute the new set of facilitators.

### 2017-10-31 paper/s4-analysis.tex
Edit paper before defence
Address unfair facilitator election

\subsection{Correctness of the Consensus Protocol}
$\Pi_c$ correctly implements the \textsc{Checo} consensus protocol (\Cref{def:consensus}) due to the following.
The agreement, validity and termination properties hold because:
\begin{itemize}
    \item The CP blocks sent to the facilitators are eventually delivered, and then ACS eventually starts.
    \item Agreement, validity and termination hold for ACS as they are the properties of ACS and are proven to hold in~\cite{miller2016honey}.
    \item The consensus result and signatures are eventually disseminated to all the nodes,
        so honest nodes must hold the same result as the honest facilitators.
\end{itemize}
Fairness holds because we model $\textsf{H}(\cdot)$ as a query to the random oracle.
Sorting nodes by the luck value $\textsf{H}(\C || pk)$ can be seen as a random permutation of a list of nodes.
Therefore every node with a CP block in the consensus result has the same probability of becoming a facilitator.

@@

\subsection{Fault Tolerance}
Finally, we consider the effect when the number of adversaries is more than $t$,
which is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
especially when $N$ is large.
Hence we are interested in the probability for this to happen under our facilitator election process.
The problem is modelled by a hypergeometric distribution,
where the random variable $X$ is the number of malicious nodes.
For our system to fail, we are interested in the following probability.
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]
$$
Let $E[X] = n\alpha$ where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n$.
Using the tail inequality found in~\cite{skala2013hypergeometric}
$$
\Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
$$
and setting 
$$
\tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha,
$$
we arrive at the following bound
$$
\Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}.
$$

The bound is not tight, but it is useful for picking parameters for the desired level of fault tolerance.
If $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, we may increase $n$ to achieve the same.
Furthermore, hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric}.
So the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ malicious nodes drops off exponentially as the expected value moves away from $\lfloor \frac{n-1}{3} \rfloor$.
To put this into perspective,
suppose $n = 100$ and $\alpha = 1/10$, i.e. 10\% of the nodes are malicious,
then the probability to elect more malicious nodes than the threshold is $9.9 \times 10^{-6}$.
% To put this into perspective,
% suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
% Then the probability to elect more malicious nodes than the threshold is only $2.6 \times 10^{-16}$.

>>>>

\subsection{Correctness of the Consensus Protocol}
$\Pi_c$ correctly implements the \textsc{Checo} consensus protocol (\Cref{def:consensus}) due to the following.
The agreement, validity and termination properties hold because:
\begin{itemize}
    \item The CP blocks sent to the facilitators are eventually delivered, and then ACS eventually starts.
    \item Agreement, validity and termination hold for ACS as they are the properties of ACS and are proven to hold in~\cite{miller2016honey}.
    \item The consensus result and signatures are eventually disseminated to all the nodes,
        so honest nodes must hold the same result as the honest facilitators.
\end{itemize}
% Fairness holds because we model $\textsf{H}(\cdot)$ as a query to the random oracle.
% Sorting nodes by the luck value $\textsf{H}(\C || pk)$ can be seen as a random permutation of a list of nodes.
% Therefore every node with a CP block in the consensus result has the same probability of becoming a facilitator.

@@

% \subsection{Fault Tolerance}
% Finally, we consider the effect when the number of adversaries is more than $t$,
% which is useful because in practice it is difficult to guarantee that $t$ satisfies $n \ge 3t + 1$,
% especially when $N$ is large.
% Hence we are interested in the probability for this to happen under our facilitator election process.
% The problem is modelled by a hypergeometric distribution,
% where the random variable $X$ is the number of malicious nodes.
% For our system to fail, we are interested in the following probability.
% $$
% \Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1]
% $$
% Let $E[X] = n\alpha$ where $0 \le \alpha \le \lfloor \frac{n-1}{3} \rfloor/n$.
% Using the tail inequality found in~\cite{skala2013hypergeometric}
% $$
% \Pr[X \ge E[X] + \tau n] \le e^{-2\tau^2n},
% $$
% and setting 
% $$
% \tau = \frac{\lfloor \frac{n-1}{3} \rfloor + 1}{n} - \alpha,
% $$
% we arrive at the following bound
% $$
% \Pr[X \ge \lfloor \frac{n-1}{3} \rfloor + 1] \le e^{-2 \big(\frac{\lfloor  \frac{n - 1}{3} \rfloor + 1}{n} - \alpha \big)^2 n}.
% $$
% 
% The bound is not tight, but it is useful for picking parameters for the desired level of fault tolerance.
% If $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
% On the other hand, if $\alpha$ is fixed, we may increase $n$ to achieve the same.
% Furthermore, hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric}.
% So the probability of picking more than $\lfloor \frac{n-1}{3} \rfloor$ malicious nodes drops off exponentially as the expected value moves away from $\lfloor \frac{n-1}{3} \rfloor$.

% TODO what's a good example?

% To put this into perspective,
% suppose $n = 100$ and $\alpha = 1/10$, i.e. 10\% of the nodes are malicious,
% then the probability to elect more malicious nodes than the threshold is $9.9 \times 10^{-6}$.

% To put this into perspective,
% suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
% Then the probability to elect more malicious nodes than the threshold is only $2.6 \times 10^{-16}$.

% TODO not unbiased! 
% workaround: Include random (dummy) block in proposal, for every facilitator

### 2017-10-31 paper/s6-conclusion.tex
Edit paper before defence
Address unfair facilitator election

In this work, we described \textsc{Checo}, an application neutral blockchain system with horizontal scalability.
Our novel data structure allows nodes to efficiently store transactions and record state using CP blocks.
The round based consensus protocol uses ACS as a building block to reach consensus on CP blocks.
The consensus result lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the simple and non-blocking transaction protocol.
Finally, we introduce a validation protocol which ensures that if an agreed fragment for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of \textsc{Checo} is that it decouples consensus and transaction validation,
which enables the desirable horizontal scalability property.

We achieve the properties described in~\Cref{sec:description}.
Namely, our protocol achieves agreement on transactions as we argued in~\Cref{sec:correctness-of-validity}.
Further, the horizontal scalability is demonstrated in~\Cref{sec:implementation},
in the ideal case as well as the worst case.
In the future, we hope to apply our system to a concrete application and evaluate its performance.

>>>>

In this work, we described \textsc{Checo}, an application neutral blockchain system with horizontal scalability.
Our novel data structure allows nodes to efficiently store transactions and record state using CP blocks.
The round based consensus protocol uses ACS as a building block to reach consensus on CP blocks.
The consensus result lets nodes elect new facilitators and create new checkpoint blocks.
To make transactions, nodes use the simple and non-blocking transaction protocol.
Finally, we introduce a validation protocol which ensures that if an agreed fragment for some transaction exists,
then nodes reach agreement on the validity of that transaction.
The novelty of \textsc{Checo} is that it decouples consensus and transaction validation,
which enables the desirable horizontal scalability property, without employing sharding.

We achieve the properties described in~\Cref{sec:description}.
Namely, our protocol achieves agreement on transactions as we argued in~\Cref{sec:correctness-of-validity}.
Validity is achieved because honest nodes run the $\textsf{get\_validity}(\cdot)$ function, which, in fact, is the validity definition.
Further, the horizontal scalability is demonstrated in~\Cref{sec:implementation},
in the ideal case as well as the worst case.

In the future, we hope to apply our system to a concrete application and evaluate its performance.
Furthermore, we plan to explore a few useful design alternatives such as open membership, total fork detection and fair facilitator election.
